---
title: '<span class="glyphicon glyphicon-fire" aria-hidden="true"></span> &nbsp;&nbsp; Smoke Located'
output: 
  rmdformats::html_docco:
    mathjax: null
    self_contained: true
always_allow_html: true
params:
  map: NA
  towers: NA
  address: NA
  inc_bearings: NA
  coords: NA
  crs: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(rmdformats)
library(leaflet)
library(leafem)
library(leaflet.extras)
library(knitr)
library(dplyr)

local_time <- Sys.time()
attr(local_time, 'tzone') <- 'Australia/Melbourne'
```

<STYLE>
.page {
  background: rgb(180,17,30);
  background: linear-gradient(180deg, rgba(180,17,30,1) 5%, rgba(248,251,251,1) 55%);
}
</STYLE>

## `r params$address[[1]]$name`

Latitude __`r params$coords$Y`__, Longitude: __`r params$coords$X`__ (CRS: `r params$crs$Name`, EPSG: `r params$crs$epsg`). 



```{r map, fig.height=4.5, fig.width=7.5}
params$map
```

There are currently `r length(unique(params$inc_bearings$sourceId))` incidents within 50 km of the `r nrow(params$towers)` towers selected.

## Observation Locations

```{r towers}
kable(params$towers)
```


`r shiny::icon('fire', lib = 'glyphicon')` This report was generated: __`r local_time`__
